### 2024-08-24 paper.tex
start with other dimension calculation

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.

\begin{lemma}
    For each \(\alpha\), \(\dim X_{\mu, \alpha}\) is blah.
\end{lemma}
\begin{proof}
    CONTINUE HERE
\end{proof}

>>>>

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
We will be interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).
Let \(s\) be the function taking integer lists to lists which sorts the input in nonincreasing order.

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    First we compute
    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
    Now, we have \(s(L) = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}, ...]\).
    Let \(L' = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., q_{i_2} + p_{i_3}, ..., q_{i_r} + p_{i_{r + 1}}]\).
    We compute 
    \[\gamma(s(L)) - \gamma()\]
    yep and so on
\end{proof}
